Recent advances in smartphone computational photography

### 2020-09-10 annotated-bibliography.tex
Updates from Overleaf

My primary two sources are \cite{Wronski2019, Liba2019}.
\begin{itemize}
\item \cite{Wronski2019} describes an algorithm to use natural hand tremor to create higher resolution images from multi-frame bursts. It has the effect of improving image resolution and noise performance.

\item \cite{Liba2019} describes a mobile camera solution leveraging existing burst imaging techniques and improving low-light performance. It builds upon work done in \cite{Hasinoff2016} and uses the burst merging algorithm from \cite{Wronski2019}.
\end{itemize}
Both of these primary sources are long and very detailed. They are written by researchers at Google.

\subsection{Background Sources}
\begin{itemize}
\item \cite{Hasinoff2016} is cited in both of the previous mentioned articles and describes an earlier multi-frame burst merging algorithm. It is used as a point of comparison by both primary sources and will be necessary background information. It is also from Google Research. I think this could end up being more of a primary source.

>>>>

My primary two sources are \cite{Wronski2019, Liba2019}.
\begin{itemize}
\item Wronski 2019 \cite{Wronski2019} describes an algorithm to use natural hand tremor to create higher resolution images from multi-frame bursts. It has the effect of improving image resolution and noise performance.

\item Liba 2019 \cite{Liba2019} describes a mobile camera solution leveraging existing burst imaging techniques and improving low-light performance. It builds upon work done in \cite{Hasinoff2016} and uses the burst merging algorithm from \cite{Wronski2019}.
\end{itemize}
Both of these primary sources are long and very detailed. They are written by researchers at Google.

\subsection{Background Sources}
\begin{itemize}
\item Hasinof 2016\cite{Hasinoff2016} is cited in both of the previous mentioned articles and describes an earlier multi-frame burst merging algorithm. It is used as a point of comparison by both primary sources and will be necessary background information. It is also from Google Research. I think this could end up being more of a primary source.
\item Barron 2017 \cite{Barron2017} is on the auto-white-balance algorithm used in \cite{Liba2019} and will be used for background information on that.
\item Wikipedia articles \cite{wiki:BayerFilter, wiki:Demosaicing, wiki:Aliasing} provide background information on Bayer filters, demosaicing, and aliasing that are necessary to explain how the algorithm in \cite{Wronski2019} improves on existing techniques.

\item \cite{blog:Wronski2018, blog:Levoy2018} are the blog posts accompanying \cite{Wronski2019, blog:Levoy2018} respectively. They provide additional information and examples of the algorithms.
